---
title: "Week 1 Exercises"
author: "Nick Hegge"
date: "July 2, 2024"
output: pdf_document
---

Please complete all exercises below WITHOUT using any libraries/packages.

# Exercise 1
Assign 10 to the variable x. Assign 5 to the variable y. Assign 20 to the variable z.

```{r ex1}

#Assign values to variables
x <- 10
y <- 5
z <- 20

```


# Exercise 2
Show that x is less than z but greater than y.

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex2}

#Single boolean expression to check if x is less than z and greater than y
result_ex2 <- x < z & x > y
result_ex2

```

# Exercise 3
Show that x and y do not equal z. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex3}

#Single boolean expression to check if x and y do not equal z
result_ex3 <- x != z & y != z
result_ex3

```


# Exercise 4
Show that the formula `x + 2y = z`. 

**Note: your output must be a SINGLE boolean**

```{r ex4}

#Check if x + 2y equals z in a single boolean expression
result_ex4 <- (x + 2 * y) == z
result_ex4

```

# Exercise 5
I have created a vector (test_vector) of integers for you. Determine if any of x, y, or z are in the vector. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**


```{r ex5}
#Check if x, y, or z are in the test_vector
test_vector <- c(1, 5, 11:22)
result_ex5 <- x %in% test_vector | y %in% test_vector | z %in% test_vector
result_ex5
```

# Exercise 6
Show which value is contained in the test vector. To do this you will need to create an element-wise logical vector using operators. `x == vector`. Once you have done that you will need to use slicing to return all indices that have matches.
**Note: your output should be two integers**

```{r ex6}

#Find which values (x, y, or z) are contained in the test_vector and their indices
matches_x <- which(test_vector == x)
matches_y <- which(test_vector == y)
matches_z <- which(test_vector == z)

#Combine all matching indices into a single vector
all_matches <- c(matches_x, matches_y, matches_z)
all_matches

```






